Handovers - SIPHER 7 Equivalent Income

### 2023-06-13 minos/validation/handovers_S7.Rmd
Properly using the "shall.we.save" boolean to decide whether to save the plots or not

ggsave(filename = 'hh_income_wav1.png',
       plot = last_plot(),
       path = save.path)

@@

spaghetti_plot(income.spag, 'hh_income',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'EI_wav1.png',
       plot = last_plot(),
       path = save.path)

@@

spaghetti_plot(ei.spag, 'equivalent_income',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'S7_housing_quality.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_housing_quality',
                 save = TRUE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_housing_quality',
               save = FALSE,
               save.path = save.path)

@@

ggsave(filename = 'S7_neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_neighbourhood_safety',
                 save = FALSE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_neighbourhood_safety',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'S7_labour_state.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = FALSE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_labour_state',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'S7_physical_health.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_physical_health',
                 save = FALSE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_physical_health',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'S7_mental_health.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_mental_health',
                 save = FALSE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_mental_health',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'loneliness.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'loneliness',
                 save = FALSE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'loneliness',
               save = TRUE,
               save.path = save.path)

@@

ggsave(filename = 'education_state.png',
       plot = last_plot(),
       path = save.path)

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = FALSE,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'education_state',
               save = TRUE,
               save.path = save.path)

>>>>

if (shall.we.save) {
  ggsave(filename = 'hh_income_wav1.png',
         plot = last_plot(),
         path = save.path)
}

@@

spaghetti_plot(income.spag, 'hh_income',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'EI_wav1.png',
         plot = last_plot(),
         path = save.path)
}

@@

spaghetti_plot(ei.spag, 'equivalent_income',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'S7_housing_quality.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_housing_quality',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_housing_quality',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'S7_neighbourhood_safety.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_neighbourhood_safety',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'S7_labour_state.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_labour_state',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'S7_physical_health.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_physical_health',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_physical_health',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'S7_mental_health.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_mental_health',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'S7_mental_health',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'loneliness.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'loneliness',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

@@

if (shall.we.save) {
  ggsave(filename = 'education_state.png',
         plot = last_plot(),
         path = save.path)
}

@@

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = shall.we.save,
                 save.path = save.path)
```

@@

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)
